The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-28 paper/sections/intro.tex
first pass over intro

The consumption of geometric surface models by physics-based animation algorithms is fraught with difficulty. 
For volumetric objects, this process often involves identifying and discretizing the interior of the modelled object, 
typically either as a tetrahedral or hexahedral mesh.%
This procedure is both expensive and difficult, especially if the surface model is constructed from higher-order boundary
representations, or if the volumetric discretization is required to be conforming or feature aligned. 
Removing explicit volumetric discretization from the physics-based-animation pipeline can avoid these difficulties and 
also provide a more unified modelling and simulation experience.

@@

Isogeometric Analysis (IGA) is a physics simulation methodology that uses the control variables of the NURBS model
as the degrees-of-freedom (DOFS) of the simulation itself. 
Unfortunately IGA approaches for volumetric objects still require background volumetric structures, typically
regular grids that make satisfaction of boundary conditions difficult (which makes collision resolution hard)
or more complicated cut-cell grids which introduce non-trivial root finding problems into the mix. 
Crucially, these simulation schemes typically assume models arise from engineering applications and meet tight geometric
criteria such as that the mesh is manufacturable. 
These inputs are much cleaner than those produced by a typical animation modeller.

@@

We present the first truly meshless (no volumetric discretization generated) algorithm for direct, nonlinear elastodynamic simulation of NURBs models. 
Our nonlinear elastodynamic simulation scheme requires only a boundary description of the object (we do not strictly require a solid model) and
approriate physical parameters.  
Because we explicitly use the NURBS boundary representation in the simulation, it is straightforward to handle
Dirichlet and Neumann boundary conditions and to apply contact resolution. 
Crucially because we broadly target animation not necessarily simulation for engineering or manufacturing, we don't require that models
satisfy the rigourous geometric requirements common for these applications

Our approach draws inspiration from the recently developed Virtual Element Method (VEM) for solving partial differential equations on domains tiled with arbitrary polygons.
We establish a connection between VEM and the well-known shape matching simulation algorithm. This allows us 
to derive equations of motion for an arbitrary curved surface model, made of NURBS, via Lagrangian Mechanics. 
Importantly, we show how to replace volumetric data structures for integration and blending weight computation with ray casting approaches which enables
our meshless approach to elastodynamic physically-based animation.

>>>>

The consumption of geometric surface models by physics-based animation algorithms is fraught with difficulty. 
For volumetric objects, this process often involves identifying and discretizing the interior of the modelled object, 
typically either as a tetrahedral or hexahedral mesh. 
This procedure is both expensive and difficult, especially if the surface model is constructed from higher-order boundary
representations, or if the volumetric discretization is required to be conforming or feature aligned. 
Removing explicit volumetric discretization from the physics-based-animation pipeline can avoid these difficulties and 
also provide a more unified modelling and simulation experience.

@@

Isogeometric Analysis (IGA) is a physics simulation methodology that uses the control variables of the NURBS model
as the degrees-of-freedom (DOFs) of the simulation itself. 
Unfortunately IGA approaches for volumetric objects still require background volumetric structures, typically
regular grids that make satisfaction of boundary conditions difficult (which makes collision resolution hard)
or more complicated cut-cell grids which introduce non-trivial root finding problems into the mix. 
Crucially, these simulation schemes typically assume models arise from engineering applications and meet tight geometric
criteria such as that the mesh is manufacturable. 
These inputs are much cleaner than those produced by a typical animation modeller.

@@

We present the first truly meshless (no volumetric discretization required) algorithm for direct, nonlinear elastodynamic simulation of NURBs models. 
Our nonlinear elastodynamic simulation scheme requires only a boundary description of the object (we do not strictly require a solid model) and
approriate physical parameters.  
Because we explicitly use the NURBS boundary representation in the simulation, it is straightforward to handle
Dirichlet and Neumann boundary conditions and to apply contact resolution. 
Crucially, because we broadly target animation not necessarily simulation for engineering or manufacturing, we don't require that models
satisfy the rigourous geometric requirements common for these applications.

Our approach draws inspiration from the recently developed Virtual Element Method (VEM) for solving partial differential equations on domains tiled with arbitrary polygons.
We establish a connection between VEM and the well-known shape matching simulation algorithm~\cite{10.1145/1073204.1073216,10.1145/2019406.2019438}. This allows us 
to derive equations of motion for an arbitrary curved surface model, made of NURBS, via Lagrangian Mechanics. 
Importantly, we show how to replace volumetric data structures for integration and blending weight computation with ray casting approaches which enables
our meshless approach to elastodynamic physically-based animation.
